---
title: "Prelab5"
author: "Shu Zhou"
date: "2020/10/28"
output: pdf_document
---

```{r setup, include=FALSE}
library(data.table)
library(ggplot2)
library(tidyr)
library(dplyr)
library(ggthemes)
library(corrplot)
library(RColorBrewer)
library(tidyverse)
library(MASS)
library(mvtnorm)
```


```{r }
##This is the Prelab5 of STATS 413
##Author: Shu Zhou
##UMID: 19342932
```

__(a.)__
Fit a multiple regression model to predict Sales using Price,
Urban, and US.
```{r}
library(ISLR)
data(Carseats)
model1<-lm(Sales~Price+Urban+US, data=Carseats)
summary(model1)
```

__(b.)__
Provide an interpretation of each coefficient in the model. Be
careful—some of the variables in the model are qualitative!

\begin{itemize}
\item{Price:} (-0.054459) unit of increase in Price would cause a 54.459 decrease in Sales, the variable Price is statistically significant.
\item {UrbanYes:} (-0.021916): Sales are 22 lower for Urban locations, the variable Urban is not statistically significant.
\item {USYes:} (1.200573): Sales are 1200.573 higher in the US locations, the variable US is statistically significant.
\end{itemize}


