---
title: "Prelab5"
author: "Shu Zhou"
date: "2020/10/28"
output: pdf_document
---

```{r setup, include=FALSE}
library(data.table)
library(ggplot2)
library(tidyr)
library(dplyr)
library(ggthemes)
library(corrplot)
library(RColorBrewer)
library(tidyverse)
library(MASS)
library(mvtnorm)
```


```{r }
##This is the Prelab5 of STATS 413
##Author: Shu Zhou
##UMID: 19342932
```

__(a.)__
Using the which function. Generate a vector Z of 100 iid standard normal variables. Use
which to find the indices for which Zi > 1.8. Print the values of Zi for these indices. Use
which to find the index of maxi Zi and maxi |Zi|.
```{r}
set.seed(1)
Z=rnorm (100,0,1)
Z_I<-which(Z>1,8)#Zi > 1.8
Z_I;Z[Z_I]# Print the values of Zi for these indices
which(Z==max(Z)) #maxi Zi
which(abs(Z)==max(abs(Z)))#maxi |Zi|
```

__(b.)__
Converting data frames to matrices. Import the Carseats dataset from the ISLR
package. Convert the variable Sales to a vector of length 400. Remove the three categorical
variables, then convert the remaining continuous variables in the dataset to a matrix of
size 400 × 7. Directly compute the estimate $\beta$ for the regression of Sales on these seven
continuous variables. (There is no need to add a column for the intercept.) (Hint: the
functions data.matrix and crossprod may be helpful here.)
```{r}
library(ISLR)
data(Carseats)
summary(Carseats)
y=Carseats$Sales
x=as.matrix(Carseats[,c(-1,-7,-10,-11)])
model_1<-lm(y~x)
solve(t(x) %*% x) %*% t(x) %*% y #directly calculate the esitmate hat(beta)
summary(model_1) #Same as directly calculate the esitmate hat(beta)
```


