---
title: "STATS 413 Hw4"
author: "Shu Zhou"
date: "2020/11/4"
output:  
    pdf_document:
    latex_engine: xelatex
    html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(ggplot2)
library(tidyr)
library(dplyr)
library(ggthemes)
library(corrplot)
library(RColorBrewer)
library(tidyverse)
library(GGally)
library(alr3)
library(MASS)
library(mvtnorm)
library(caret)
library(class)
library(ISLR)
```


This is the Assignment 4 of STATS 413
Author: Shu Zhou
UMID: 19342932


\section{Exercise 5.17}
__(5.17.1.)__
```{r}
data("salary")
cols <- character(nrow(salary))
cols[] <- "black"
cols[salary$Sex == 1] <- "red"
cols[salary$Sex == 0] <- "blue"
pairs(salary[,c(1:6)],col = cols, main = "Scatter plot of the salary data")
```

In this plot we use blue points to represent Males and red points to represent females. 
From this plot, we can see that
\begin{itemize}
\item Females generally have fewer years in rank. 
\item The variance of salary is much higher with a person who own a master's degree. 
\item Females generally have a lower salary than males.
\item The mean function of YSdeg might have a different slope for males and females.
\end{itemize}
__(5.17.2)__
```{r}
salary<-read.csv("salary.csv")
salary<-as.data.frame(salary)
summary(lm(salary~sex,data= salary))
```
The significance level is 0.0706. Hence the sex factor is not statistically significant, we cannot reject the null hypothesis with 95% of confidence. The point estimate of the Sex effect is $3340 in favor of men.
__(5.17.3)___
```{r}
model1<-lm(salary~.,data= salary)
summary(model1)
confint(model1)["sexMale", , drop=FALSE]
```
We can see that the sex effect is much higher for females with higher salaries. Although we cannot reject
our null hypothesis according to P-value, we cannot say that sex has no impact.

__(5.17.4)___
```{r}
model2<-lm(salary~.-rank,data= salary)
summary(model2)
```
After the factor degree is excluded, we can see that the most variables become less significant.
Hence we can argue that this sample is not unbiased and it is not a good choice to rely on this sample.


\section{Exercise 8.3}

__(8.3.1)__
```{r}
water<-read.csv("water.csv")
cor(water)
pairs(water[ , 2:9])
```
\begin{itemize}
\item The correlations between "OPBPC", "OPRC","OPSLAKE" and "BSAAM" are very high.
\item The correlations between year and other variables are low.
\item The correlations between "APMAM", "APSAB" and "APSLAKE" are high but not as high as the "O" variables.
\end{itemize}

__(8.3.2)__
```{r}
summary(ans <- powerTransform( as.matrix(water[ , 3:8]) ~ 1))
```
The transformation we found appear to achieve linearity. Since the p-value for the 
LR-test is 0.48716.

```{r}
pairs(log(water[ , 3:9]))
```

__(8.3.3)__
```{r}
model3 <- lm(BSAAM ~ log(APMAM) + log(APSAB) + log(APSLAKE) + log(OPBPC) + log(OPRC) + log(OPSLAKE), water)
invResPlot(model3)
```
The fitted line for $\hat{\lambda}$ have the smallest RSS, hence it is the best fit, which indicates that
 the log transform is reasonable.
 
 __(8.3.4)__
```{r}
model4 <- lm(formula = log(BSAAM) ~ log(APMAM) + log(APSAB) + log(APSLAKE) +
log(OPBPC) + log(OPRC) + log(OPSLAKE), data = water)
summary(model4)
```
The two negative estimates are log(APMAM) and log(APSAB). Both of them are not significant. The negative signs are caused 
by the correlations of other included regressors.

__(8.3.5)__
```{r}
water$geometricmean_O<-rowSums(water[,6:8])/3
model5 <- lm(log(BSAAM) ~ log(APMAM) + log(APSAB) + log(APSLAKE) +geometricmean_O , water)
anova(model5,model4)
```
Hence, we can reject that the three "O" log predictors are not equal ,i.e. they are equal.
Which shows that the geometric mean of the snow depth represents its valley as well as do the individual measurements.
```{r}
water$geometricmean_A<-rowSums(water[,3:5])/3
model6 <- lm(log(BSAAM) ~ log(OPBPC) + log(OPRC) + log(OPSLAKE) +geometricmean_A , water)
anova(model6,model4)
```
Hence, we cannot reject that the three "A" log predictors are not equal. 
Which shows that each "A" log predictor measurement is important.
