---
title: "Prelab4"
author: "Shu Zhou"
date: "2020/9/30"
output: pdf_document
---

```{r setup, include=FALSE}
library(data.table)
library(ggplot2)
library(tidyr)
library(dplyr)
library(ggthemes)
library(corrplot)
library(RColorBrewer)
library(tidyverse)
library(MASS)
library(mvtnorm)
```


```{r }
##This is the Prelab4 of STATS 413
##Author: Shu Zhou
##UMID: 19342932
```

__(a.)__
```{r}
set.seed (1)
x=rnorm (100)
y=2*x+rnorm (100)
summary(lm(y~x + 0))
```

$\hat{\beta_{x}} = 1.9939$, $Std.err = 0.1065$, $t-statistic = 18.73$, $P-value = 2e-16$
The residual standard error is almost not related to the coefficient estimate.
The p-value is statistically significant.


__(b.)__
```{r}
summary(lm(x ~ y + 0))
```
$\hat{\beta_{x}} =  0.39111$, $Std.err = 0.02089$, $t-statistic = 18.73$, $P-value = 2e-16$
The residual standard error is almost not related to the coefficient estimate.
The p-value is statistically significant.


__(c.)__
The t-value and p-statistic are the same, only the estimate of coefficients are different,
which reflects the relationship
$y = 2x + \varepsilon$

